Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-13 paper/aldebaran.tex
More edits to time-series analysis section.

Here we have adopted the \citet{Kelly2014} approach.  The \texttt{CARMA.jl} package\footnote{\url{https://github.com/farr/CARMA.jl}} implements Kalman filters that can compute the likelihood for a set of observations parameterised by either the roots $r_i$ and $b_j$ or the RMS amplitudes $A_i$ and roots $r_i$.  Because we have a set of observations taken with different instruments at different sites (see Section \ref{sec:archival-obs}), we include RV offset (i.e.\ mean value) parameters that are site-dependent and also a site-dependent scaling parameter.  Thus, the $i$th RV measured at site $j$ is assumed to be
\begin{equation}
\label{eq:RV-model}
y_{ij} = v_r\left(t_i\right) + \mu_j + y\left( t_i \right) + \nu_j \epsilon_{ij},
\end{equation}
$t_i$ is the time of the measurement, $v_r$ is a planetary RV signal \citep{Hatzes2015}, $\mu_j$ is the site-dependent mean RV offset, $y(t)$ is the CARMA process representing stellar activity, $\nu_j$ is the site-dependent uncertainty scaling parameter, and $\epsilon_{ij}$ is an independent Gaussian random variable with mean zero and standard deviation equal to the quoted uncertainty of the observation.  We impose broad priors (see Table \ref{tab:parameters}) on the parameters of the planetary RV signal, the CARMA process, the $\mu_j$ offsets, and the $\nu_j$ scale factors.

\begin{deluxetable}{lll}
\tablecolumns{3}
\tablecaption{\label{tab:parameters} The parameters in our model (see Eq.\ \eqref{eq:RV-model}).}
\tablehead{\colhead{Parameter} & \colhead{Prior} & \colhead{Description}}
\startdata
$\mu_j$ & Normal\tablenotemark{a} & The per-site RV offset. \\
\enddata
\tablenotetext{a}{The prior for $\mu_j$ is centered on the mean of the data from site $j$ and has standard deviation 10 times the standard deviation of the data.}
\end{deluxetable}

>>>>

Here we have adopted the \citet{Kelly2014} approach.  The \texttt{CARMA.jl} package\footnote{\url{https://github.com/farr/CARMA.jl}} implements Kalman filters that can compute the likelihood for a set of observations parameterised by either the roots $r_i$ and $b_j$ or the RMS amplitudes $A_i$ and roots $r_i$.  Because we have a set of observations taken with different instruments at different sites (see Section \ref{sec:archival-obs}), we include RV offset (i.e.\ mean value) parameters that are site-dependent and also a site-dependent scaling parameter.  Thus, the $i$th RV measured at site $j$, $y_{ij}$, is assumed to be
\begin{equation}
\label{eq:RV-model}
y_{ij} = v_r\left(t_i\right) + \mu_j + y\left( t_i \right) + \nu_j \epsilon_{ij},
\end{equation}
$t_i$ is the time of the measurement, $v_r$ is a planetary RV signal \citep{Hatzes2015,Gregory2005}, $\mu_j$ is the site-dependent mean RV offset, $y(t)$ is the CARMA process representing stellar activity, $\nu_j$ is the site-dependent uncertainty scaling parameter, and $\epsilon_{ij}$ is an independent Gaussian random variable with mean zero and standard deviation equal to the quoted uncertainty of the observation.  We impose broad priors (see Table \ref{tab:parameters}) on the parameters of the planetary RV signal, the CARMA process, the $\mu_j$ offsets, and the $\nu_j$ scale factors.

\begin{deluxetable}{lll}
\tablecolumns{3}
\tablecaption{\label{tab:parameters} The parameters in our model (see Eq.\ \eqref{eq:RV-model}).}
\tablehead{\colhead{Parameter} & \colhead{Prior} & \colhead{Description}}
\startdata
\cutinhead{Per-Site RV Offset and Uncertainty Scaling}
$\mu_j$ & $N\left[ \left\langle y_{j} \right\rangle, 10 \sigma_{y_{j}} \right] \left( \mu _j \right)\tablenotemark{a}$ & The per-site RV offset. \\
$\nu_j$ & $1/\nu_j, \quad \nu_j \in [1/2, 2]$ & The per-site uncertainty scale factor. \\
\cutinhead{Keplerian Parameters}
$K$ & $1/K, \quad K \in \left[ \min_j \sigma_{y_j}/100, \max_j 10 \sigma_{y_j} \right]$ & RV semi-amplitude. \\
$P$ & $1/P, \quad P \in [600, 700] \, \mathrm{d}$ & Keplerian period \\
$e$ & $2e$\tablenotemark{b} & Keplerian eccentricity \\
$\omega$ & $\mathrm{const}$ & Longitude of pericentre \\
$\chi$ & $\mathrm{const}$ & Pericentre passage is at $t = \chi P$\\
\enddata
\tablenotetext{a}{$\left\langle y_j \right\rangle$ and $\sigma_{y_j}$ are the mean and standard deviation of the RV timeseries from site $j$.}
\tablenotetext{b}{We actually sample in and impose a (flat) prior on $x \equiv e \cos \omega$ and $y \equiv e \sin \omega$.}
\end{deluxetable}
